FAIR fission track analysis with geochron@home

### 2025-07-23 geochron@home/manuscript/paper.tex
Updated author contributions

\Author[1][p.vermeesch@ucl.ac.uk]{Pieter}{Vermeesch}
\Author[1]{Tim}{Band}
\Author[2]{Jiangping}{He}
\Author[3]{Andrew}{Carter}
\Author[1]{Rex}{Galbraith}

@@

\authorcontribution{Pieter Vermeesch designed the study, acquired the
  funding, counted fission tracks and wrote the paper. Jiangping He
  created geochron@home. Tim Band expanded geochron@home and wrote the
  accompanying microscope image acquisition software. Andrew Carter
  provided the samples, prepared the training data and counted fission
  tracks. Rex Galbraith derived Equation~\ref{eq:NO} and verified all
  the other calculations.}

>>>>

\Author[1][p.vermeesch@ucl.ac.uk]{Pieter}{Vermeesch}
\Author[1]{Tim}{Band}
\Author[2]{Jiangping}{He}
\Author[1]{Rex}{Galbraith}
\Author[3]{Andrew}{Carter}

@@

\authorcontribution{PV designed the study, acquired the funding and
  counted fission tracks. JH created geochron@home. TB expanded
  geochron@home and wrote the accompanying microscope image
  acquisition software. RG derived Equation~\ref{eq:NO} and verified
  the other calculations. AC provided the samples, prepared the
  training data and counted fission tracks. PV and RG wrote the paper
  with input from the other authors.}
